DDL:
1) Create a table named products with the following columns:
• product_id (INT, primary key)
• product_name (VARCHAR(100))
• price (DECIMAL(10,2))

create table products(product_id Int,
Product_name varchar(100),
Price decimal(10,2),
Primary key(product_id));

2) Add a column stock_quantity (INT) to the products table.
Alter table products
add column stock_quantity INT;

3) Rename the column price in the products table to product_price.

Alter table products
rename column price to product_price;

4) Change the datatype of the product_name column to VARCHAR(150) in the products table.

alter table products
modify column product_name  varchar(150);

5) Remove the column stock_quantity from the products table.
alter table products
drop column stock_quantity;

6) Delete the products table from the database.
drop table products;

7) Truncate the products table to remove all rows but keep the table structure.
Truncate table products;

8) Create a new table customers with the following columns:
customer_id (INT, primary key)
first_name (VARCHAR(50))
last_name (VARCHAR(50))
email (VARCHAR(100), must be unique);

create table customers(
customer_id int,
first_name varchar(50),
last_name varchar(50),
email varchar(100),
unique(email),
primary key(customer_id));

9) Create a foreign key fk_customer_id in the orders table that references the customer_id
column in the customers table.

create table orders(order_id int,
order_Number int,
primary key(order_id),
customer_id int,
Foreign key(customer_id) references customers(customer_id));

-------------------------------
DML
10) Insert a new product into the products table with the following data:
• product_id: 1
• product_name: 'Laptop'
• product_price: 999.99


Insert into products(product_id,Product_name,product_price)values(1,'Laptop',999.99);

11) Insert multiple rows into the products table with the following data:
(2, 'Smartphone', 499.99)
(3, 'Tablet', 299.99)

Insert into products(product_id,Product_name,product_price)values(2,'Smartphone',499.99),(3,'Tablet',299.99);

12) Update the price of the product with product_id 1 to 1099.99

update products
set product_price = 1099.99
where product_id =1;

13) Increase the price of all products by 10%.
update products
set product_price = product_price*0.1;

14) Delete the product with product_id =3 3 from the products table.

delete from products
where product_id =3;

15) Insert a new customer into the customers table with the following data:
• customer_id: 1
• first_name: 'John'
• last_name: 'Doe'
• email: 'john.doe@example.com'

Insert into customers(customer_id,first_name,last_name,email)values(1,'John','Doe','john.doe@example.com');

16) Insert multiple customers into the customers table:
(2, 'Jane', 'Smith', 'jane.smith@example.com')
(3, 'Bob', 'Johnson', 'bob.johnson@example.com')

Insert into customers(customer_id,first_name,last_name,email)values(2,'Jane','Smith','jane.smith@example.com'),
(3,'Bob','johnson','bob.johnson@example.com');

17) Update the email of the customer with customer_id 2 to new.email@example.com.

update customers
set email = 'new.email@example.com'
where customer_id = 2;

18) Delete the customer with customer_id 3 from the customers table.

delete from customers
where customer_id ='3';
19) Update the first name of all customers with the last name Smith to Emily.
update customers
set first_name = 'Smith',
last_name = 'Emily'